---
title: "Supplementary material for \"Uprooting sub-standard visualisation practices for decision-making in operational management\""
output:
  bookdown::html_document2:
    code_folding: "hide"
    theme: "paper"
    code_download: true
    number_sections: false
---

To see the code, click on the CODE button. You can also download the whole R Markdown file from the drop down menu on the top right corner. 

```{r setup, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggtext)
library(patchwork)
library(readxl)
library(nullabor)
library(here)
library(janitor)
library(scales)
#theme_set(theme_classic())
knitr::opts_chunk$set(fig.path = "images/",
                      dev = c("png", "pdf", "svg"))
```


```{r data}
df_full <- read_xlsx(here("data/MaskedCoverage-Fig3.xlsx")) %>% 
  clean_names() %>% 
  add_row(state = c("OR", "WY", "SD", "WV", "DC", "AL")) %>% 
  mutate(row = case_when(
    state %in% c("ME") ~ 1L,
    state %in% c("VT", "NH") ~ 2L,
    state %in% c("WA", "ID", "MT", "ND", "MN", "IL", "WI", "MI", "NY", "RI", "MA") ~ 3L,
    state %in% c("OR", "NV", "WY", "SD", "IA", "IN", "OH", "PA", "NJ", "CT") ~ 4L,
    state %in% c("CA", "UT", "CO", "NE", "MO", "KY", "WV", "VA", "MD", "DE") ~ 5L,
    state %in% c("AZ", "NM", "KS", "AR", "TN", "NC", "SC", "DC") ~ 6L,
    state %in% c("OK", "LA", "MS", "AL", "GA") ~ 7L,
    state %in% c("TX", "FL") ~ 8L,
                         TRUE ~ 0L),
    col = case_when(
      state %in% c("WA", "OR", "CA") ~ 1L,
      state %in% c("ID", "NV", "UT", "AZ") ~ 2L,
      state %in% c("MT", "WY", "CO", "NM") ~ 3L,
      state %in% c("ND", "SD", "NE", "KS", "OK", "TX") ~ 4L,
      state %in% c("MN", "IA", "MO", "AR", "LA") ~ 5L,
      state %in% c("IL", "IN", "KY", "TN", "MS") ~ 6L,
      state %in% c("WI", "OH", "WV", "NC", "AL") ~ 7L,
      state %in% c("MI", "PA", "VA", "SC", "GA") ~ 8L,
      state %in% c("NY", "NJ", "MD", "DC", "FL") ~ 9L,
      state %in% c("VT", "RI", "CT", "DE") ~ 10L,
      state %in% c("ME", "NH", "MA") ~ 11L,
      TRUE ~ 0L
    ))

df_miss <- df_full %>% 
  filter(!is.na(readmission_rate))
```

(ref:mimicary) This figure recreates Figure 3 in Basole et al.

```{r mimic-original, fig.height = 8, fig.width = 18, fig.cap = "(ref:mimicary)"}
g1 <- ggplot(df_miss, aes(col, row)) +
  geom_point(aes(size = coverage_obscured, color = readmission_rate * 100), alpha = 0.8) +
  geom_text(data = df_full, aes(label = state), color = "black", nudge_y = 0.05) +
  geom_text(aes(label = percent(readmission_rate, 0.01)), nudge_y = -0.1, size = 2.5) +
  theme_void() +
  scale_color_gradient2(low = "#3F6E9A", high = "#AB4C30", midpoint = median(df_miss$readmission_rate * 100), mid = "#E7D9C6") +
  scale_size(range = c(3, 30)) +
  scale_y_reverse() +
  theme(plot.margin = margin(r = 30)) +
  labs(color = "Readmission",
       size = "Coverage")

g2 <- ggplot(df_miss, aes(col, row)) +
  geom_point(aes(size = coverage_obscured, color = colorectal_cancer_screenings), alpha = 0.8) +
  geom_text(data = df_full, aes(label = state), color = "black", nudge_y = 0.05) +
  geom_text(aes(label = percent(colorectal_cancer_screenings/100, 0.01)), nudge_y = -0.1, size = 2.5) +
  theme_void() +
  scale_color_gradient2(low = "#3F6E9A", high = "#AB4C30", midpoint = median(df_miss$colorectal_cancer_screenings), mid = "#E7D9C6") +
  scale_size(range = c(3, 30)) +
  scale_y_reverse()  +
  labs(color = "Cancer Screening",
       size = "Coverage")

g1 + g2 + plot_layout(guides = "collect") 
```

(ref:fig3-alt) This is an alternative graph design for Figure \@ref(fig:mimic-original).

```{r fig3-alt, fig.height = 4, fig.width = 8, fig.cap = "(ref:fig3-alt)"}
theme_set(theme_classic())
g1 <- ggplot(df_miss, aes(coverage_obscured * 100, colorectal_cancer_screenings)) +
  geom_point() +
  labs(x = "Coverage (%)", y = "Cancer Screening (%)") +
  geom_smooth(method = loess, formula = y ~ x) +
  annotate("richtext", x = 80, y = 73, label.color = NA, fill = "transparent", label = glue::glue("R<sup>2</sup> = {scales::comma(cor(df_miss$coverage_obscured, df_miss$colorectal_cancer_screenings), 0.001)}")) 

g2 <- ggplot(df_miss, aes(coverage_obscured * 100, readmission_rate * 100)) +
  geom_point() +
  labs(x = "Coverage (%)", y = "Readmission (%)") +
  geom_smooth(method = loess, formula = y ~ x) +
  annotate("richtext", x = 80, y = 15.3, label.color = NA, fill = "transparent", label = glue::glue("R<sup>2</sup> = {scales::comma(cor(df_miss$coverage_obscured, df_miss$readmission_rate), 0.001)}")) 

g1 + g2 
```

```{r lineup-data}
set.seed(2021)
lineup_data <- null_permute("colorectal_cancer_screenings") %>% 
  lineup(true = df_miss, n = 20, pos = 3)
```

(ref:lineup-theirs) The lineup for the tile grid plot.

```{r lineup-theirs, fig.height = 10, fig.width = 10, fig.cap = "(ref:lineup-theirs)"}
ggplot(lineup_data, aes(col, row)) +
  geom_point(aes(size = coverage_obscured, color = colorectal_cancer_screenings), alpha = 0.8) +
  theme_void() + 
  scale_color_gradient2(low = "#3F6E9A", high = "#AB4C30", midpoint = median(df_miss$colorectal_cancer_screenings), mid = "#E7D9C6") +
  scale_size(range = c(1, 5)) +
  scale_y_reverse(expand = c(0.1, 0.2))  +
  guides(color = "none", size = "none") + 
  facet_wrap(~.sample, ncol = 5) +
  scale_x_continuous(expand = c(0.1, 0.1)) + 
  theme(legend.position = "bottom",
        strip.text = element_text(size = 18, margin = margin(t = 3, b = 3)),
        strip.background = element_rect(color = "black", size = 1.5))
```

(ref:lineup-ours) The lineup for the scatter plot.

```{r lineup-ours, fig.height = 10, fig.width = 10, fig.cap = "(ref:lineup-ours)"}
ggplot(lineup_data, aes(coverage_obscured * 100, colorectal_cancer_screenings)) +
  geom_point() +  
  geom_smooth(method = loess, formula = y ~ x) +
  facet_wrap(~.sample, ncol = 5) +
  scale_x_continuous(expand = c(0.1, 0.1)) + 
  theme(legend.position = "bottom",
        strip.text = element_text(size = 18, margin = margin(t = 3, b = 3)),
        strip.background = element_rect(color = "black", size = 1.5),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks.length = unit(0, "pt"))
```



# Acknowledgement 

We thank the Basole et al. for supplying us the synthetic data to draw the above plots. 

# Session Information


```{r session-info}
sessioninfo::session_info()
```

